---
title: "API Notebook"
output: html_notebook
---

**Feb 15, 2021:**
- Joined the Project repo: https://github.com/Conrad-Yeung/Data534-Project-Group8
  - Includes MIT License and README.md
- Created Notebook-Aamir file
- Found our API: https://rawg.io/apidocs
- Wrote a small code patch to get data from API and clean it

```{r}
library(httr)
library(jsonlite)
library(tibble)
library(tidyr)
library(dplyr)
library(stringr)
library(purrr)

# Getting the data
url <- "https://api.rawg.io/api/games?key=bb91c5797154447483ea1dda3f17574e&page_size=20&page=3"
resp <- httr::GET(url)
cont_raw <- httr::content(resp)
str(cont_raw, max.level = 3, list.len = 4)

# Parsing the data
data_raw_ugly <- jsonlite::fromJSON(rawToChar(resp$content))
glimpse(data_raw_ugly, max.level = 3, list.len = 4)

data_raw <- enframe(unlist(cont_raw))
data_raw

data_raw %>% separate(name, into = c(paste0("x", 1:10)))

data_raw %>% separate(name, into = c(paste0("x", 1:10)), fill = "right")

rgx_split <- "\\."
n_cols_max <-
  data_raw %>%
  pull(name) %>% 
  str_split(rgx_split) %>% 
  map_dbl(~length(.)) %>% 
  max()
n_cols_max

nms_sep <- paste0("name", 1:n_cols_max)
data_sep <-
  data_raw %>% 
  separate(name, into = nms_sep, sep = rgx_split, fill = "right")
data_sep
```

**Feb 16, 2021**
- We chose Conrad work for data acquisition and munging.
- Worked on the readme.md file
- Created project file structure.
- Working on one version of get genre function.

```{r}
source("extract_as.df_RAWG.R")
source("get_game_list.R")
source("parse_RAWG.R")

link <- get_game_list(n=40, page=1, api_key="95731a37dcf84a638308f6f40fb01801")
raw <- parse_RAWG(link)
df <- extract_as.df_RAWG(raw)
link
```


```{r}
API_KEY = "95731a37dcf84a638308f6f40fb01801"
get_genre_list <- function(genre_name=NULL){
  #' @title Search and return list of games in a genre from RAWG 
  #'
  #' @description Use API to get all data on a genre and display
  #'
  #' @importFrom json fromJSON
  #' @import docstring
  #' 
  #' @param genre_name: String containing the genre name
  #'
  #' @return Returns a data frame object containing the list of games of a particular genre
  #'
  #' @examples df <- get_genre_list("action")
  

  
  # if(!is.null(genre_name)) {
  #   print(genre_name)
  # }


  #Return object
  return(df_genre)
}
# df <- get_genre_list("action")
# df

base <- "https://api.rawg.io/api/genres"
link <- paste0(base,'?key=',API_KEY)
get_object <- httr::GET(link)
raw <- parse_RAWG(get_object)
# df_genre <- extract_as.df_RAWG(raw)  # Don't try, breaks the system
```


**Feb 17, 2021**
- Had several issues with GitHub merging and pull requests.
- Worked on the vignettes. Walk-through examples to work with the package.
- Created graphs for the query results.


































