---
title: "API Notebook"
output: html_notebook
---

IDEA: Functions to get and process data (General Games list, Genre)
- Functions to visualize data (summary)
- Test functions + Travis CI

**Feb 15, 2021:**
- Created Project repo: https://github.com/Conrad-Yeung/Data534-Project-Group8
  - Includes MIT License and README.md
- Created Notebook file (obviously)
- Found our API: https://rawg.io/apidocs
- Wrote the code below: Get + Data Wrangling

What do we need to do:
- Make this a function
- Break it up into call + data wrangle
- Need to take # of games as parameter, will need to parse pages accordingly *MAX 40 ENTRIES PER PAGE*
```{r}
library(httr)
library(jsonlite)
library(dplyr)
library(tibble)
links <- GET("https://api.rawg.io/api/games?page_size=5&page=1&dates=2000-01-01,2020-12-31&genre=1,2,3&ordering=-added")
raw_content <- fromJSON(content(links,"text",encoding="UTF-8"),simplifyVector=FALSE)
results <- (raw_content$results)

#Initial Run
#Cleanup & Table values for A FIRST GAME 
data_raw <- results[[1]]
names <- enframe(unlist(data_raw))
temp_df <- data.frame(names)
temp_df <- temp_df[!grepl("tags|screenshots|store|image|requirements|clip", temp_df$name),]
#Create Unique Labeling - prepping for merge
uniquify_list <- c("ratings.id","platforms.platform.id","parent_platforms.platform.id","genres.id")
stop_list <- c("ratings.percent","platforms.released_at","parent_platforms.platform.slug","genres.games_count")
ids <- ""
for (i in 1:length(temp_df$name)){
  if (temp_df$name[i] %in% uniquify_list){
    print(temp_df$name[i])
    ids <- temp_df[i,"value"]
  }else if (temp_df$name[i] %in% stop_list){
    temp_df$name[i]<-paste(temp_df$name[i],ids,sep="")
    ids<-""
  }
  temp_df$name[i]<-paste(temp_df$name[i],ids,sep="")
}
final_df<-temp_df

#For all other n-1 games
for (entries in (2:length(results))){ #Do the same for all other N-1 games 
  #Cleanup & Table values for A SINGLE GAME 
  data_raw <- results[[entries]]
  names <- enframe(unlist(data_raw))
  temp_df <- data.frame(names)
  temp_df <- temp_df[!grepl("tags|screenshots|store|image|requirements|clip", temp_df$name),]
  
  #Create Unique Labeling - prepping for merge
  ids<-""
  for (i in 1:length(temp_df$name)){
    if (temp_df$name[i] %in% uniquify_list){
      ids <- temp_df[i,"value"]
    }else if (temp_df$name[i] %in% stop_list){
      temp_df$name[i]<-paste(temp_df$name[i],ids,sep="")
      ids<-""
    }
    temp_df$name[i]<-paste(temp_df$name[i],ids,sep="")
  }
  final_df<-full_join(final_df, temp_df, by = "name") #Joining by 'name' column
}

#Cleaning up Data.frame
final_df<-t(final_df)
colnames(final_df) <- final_df[1,]
final_df<-final_df[-1,]
rownames(final_df)<-NULL
```
**Feb 16, 2021**
-Created Notebook Repo
-Break above down into 3 functions:
  1) Function to create link based on params & GET request : get_game_list.R
  2) Parse the request into a JSON: parse_RAWG.R
  3) Wrangle to JSON into a data frame: extract_as.df_RAWG.R
-All 3 functions will be in a package called game_list.R (for parsing general game info)
```{r}
library(docstring)
library(httr)
library(dplyr)
library(tibble)
get_game_list <- function(n=40,page=1,api_key="",start_date="",end_date="",metacritic="",platform="",platform_count="",genre="",ordering=""){
  #' GET request to RAWG
  #'
  #' Submit RAWG query and receive RAWG response
  #'
  #' @importFrom httr GET
  #'
  #' @param n (int): number of games/entries (default = 40). Max 40. If you want to look at entries beyond the 40th index, use the `page` parameter.
  #' @param page (int): page number queried (default = 1) 
  #' @param api_key (str): your api key (recommended - not required, default = none)
  #' @param start_date (str): start release date in the form YYYY-MM-DD (default = none). Ex: "2020-01-30"
  #' @param end_date (str): end release date in the form YYYY-MM-DD (default = none). Ex: "2021-30-30"
  #' @param metacritic (str): metacritic rating range (default = none). Ex: "80,100" will give you ratings between 80 and 100.
  #' @param platforms (str):  ID of platform (1=XboxOne, 2=Playstation, 3=Xbox, 4=PC etc.) Ex: "1" or "1,2,3" for a range of platforms.  
  #' @param platform_count (int): number of platforms games are available on. 
  #' @param genre (str): the genre of games in the form of string or using the ID tag. Ex: "action,indie" or "4,51"
  #' @param ordering (str): how to order data, use "-" to reverse order. Ex: "name", "released", "created", "added", "updated", "rating", "-metacritic." 
  #'
  #' @return Large list containing response from RAWG query
  #'
  #' @examples 
  #' get_game_list(start_date="2000-01-01",end_date="2020-12-31",genre="1,2,3",ordering ="-added")
  #' test<-get_game_list()
  
  #Check for insertion attacks
  if (TRUE %in% grepl("&|%",c(n,page,api_key,start_date,end_date,metacritic,platform,platform_count,genre,ordering))){
    stop("Please do not try to mess with the GET request.")
  }
  
  #Check n <= 40
  if (n > 40){
    stop("Max query length is 40. If you want to get entries beyond the 40th game, please change the `page` number. For example, entry 41-80 use `page='2'.")
  } else {
    cleaned_n <- paste("page_size=",n,sep="")
  }
  
  #Page number
  cleaned_page<-paste("&page=",page,sep="")
  
  #Check if API Key is given
  if (api_key == ""){
    cleaned_api_key <- ""
  } else {
    cleaned_api_key <- paste("&key=",api_key,sep="")
  }
  
  #Check if dates are given
  if ((start_date == "")&(end_date=="")){ #No Dates Given
    cleaned_date <- ""
  }else if ((start_date != "") & (end_date=="")){ #Only Start Date Given
    stop("You need to enter an end date")
  }else if ((start_date == "") & (end_date!="")){
    stop("You need to enter an start date") #Only Start Date Given
  }else { #Both Dates given
    if ((grepl("[0-9]{4}-[0-9]{2}-[0-9]{2}",start_date) & grepl("[0-9]{4}-[0-9]{2}-[0-9]{2}",end_date)) == TRUE){
      if (start_date >= end_date){
        stop("start_date must be before end_date")
      }else{
      cleaned_date <- paste("&dates=",start_date,",",end_date,sep="")
      }
    } else {
      stop("Please enter dates in the form YYYY-MM-DD.")
    }
  }
    
  #Metacritic range
  if (metacritic == ""){
    cleaned_metacritic<-""
  }else{
    cleaned_metacritic <- paste("&metacritic=",metacritic,sep="") 
    }
  
  #Platforms
  if (platform == ""){
    cleaned_plat<-""
  }else{
    cleaned_plat <- paste("&platforms=",platform,sep="")
    }
  
  #Platform count 
  if (platform_count == ""){
    cleaned_plat_count<-""
  }else{
    cleaned_plat_count <- paste("&platforms_count=",platform_count,sep="")
    }
  
  #Genre
  if (genre == ""){
    cleaned_genre<-""
  }else{
    cleaned_genre <- paste("&genre=",genre,sep="")
    }
  
  #Ordering
  if (ordering == ""){
   cleaned_order <- "" 
  }else if (ordering %in% c("name","released","added","created","updated","rating","metacritic","-name","-released","-added","-created","-updated","-rating","-metacritic")){
    cleaned_order <- paste("&ordering=",ordering,sep="")
  }else{
    stop('Field must be one of the following: "name","released","added","created","updated","rating","metacritic","-name","-released","-added","-created","-updated","-rating","-metacritic"')
  }
  
  link <- paste("https://api.rawg.io/api/games?",cleaned_n,cleaned_page,cleaned_api_key,cleaned_metacritic,cleaned_date,cleaned_metacritic,cleaned_plat,cleaned_plat_count,cleaned_genre,cleaned_order,sep="")
  get_link <- GET(link)
  return(get_link)
}

parse_RAWG <- function(get_object){
  #' @title parse the GET request from RAWG 
  #'
  #' @description Convert the GET request from the get_game_list function into a JSON object, making the data available for extraction.
  #'
  #' @importFrom json fromJSON
  #' @import docstring
  #' 
  #' @param get_object (list): Object returned from the GET function
  #'
  #' @return Returns a JSON object containing some general summary data as well as requested data
  #'
  #' @examples raw_data <- parse_RAWG(test)

  raw_content <- fromJSON(content(get_object,"text",encoding="UTF-8"),simplifyVector=FALSE)
  
  #Return object
  return(raw_content)
}

extract_as.df_RAWG <- function(parse_object){
  #' @title extract data from the RAWG JSON object
  #'
  #' @description Extracting the data from 'results' into a dataframe, removing certain fields such as images,screenshots, stores and tags
  #' 
  #' @param parse_object (list): JSON object obtained from the parse_RAWG function
  #' 
  #' @return Returns a dataframe containing the extracted data from the GET function
  #' 
  #' @examples df <- extract_as.df_RAWG(raw_data)
  
  results <- (parse_object$results)
  
  #Initial Run
  #Cleanup & Table values for A FIRST GAME 
  data_raw <- results[[1]]
  names <- enframe(unlist(data_raw))
  temp_df <- data.frame(names)
  temp_df <- temp_df[!grepl("tags|screenshots|store|image|requirements|clip", temp_df$name),]
  #Create Unique Labeling - prepping for merge
  uniquify_list <- c("ratings.id","platforms.platform.id","parent_platforms.platform.id","genres.id")
  stop_list <- c("ratings.percent","platforms.released_at","parent_platforms.platform.slug","genres.games_count")
  ids <- ""
  for (i in 1:length(temp_df$name)){
    if (temp_df$name[i] %in% uniquify_list){
      ids <- temp_df[i,"value"]
    }else if (temp_df$name[i] %in% stop_list){
      temp_df$name[i]<-paste(temp_df$name[i],ids,sep="")
      ids<-""
    }
    temp_df$name[i]<-paste(temp_df$name[i],ids,sep="")
  }
  final_df<-temp_df
  
  #For all other n-1 games
  for (entries in (2:length(results))){ #Do the same for all other N-1 games 
    #Cleanup & Table values for A SINGLE GAME 
    data_raw <- results[[entries]]
    names <- enframe(unlist(data_raw))
    temp_df <- data.frame(names)
    temp_df <- temp_df[!grepl("tags|screenshots|store|image|requirements|clip", temp_df$name),]
    
    #Create Unique Labeling - prepping for merge
    ids<-"" #RESET THE LABEL AFTER EACH GAME
    for (i in 1:length(temp_df$name)){
      if (temp_df$name[i] %in% uniquify_list){
        ids <- temp_df[i,"value"]
      }else if (temp_df$name[i] %in% stop_list){
        temp_df$name[i]<-paste(temp_df$name[i],ids,sep="")
        ids<-""
      }
      temp_df$name[i]<-paste(temp_df$name[i],ids,sep="")
    }
    final_df<-full_join(final_df, temp_df, by = "name") #Joining by 'name' column
  }
  
  #Cleaning up Data.frame
  final_df<-t(final_df)
  colnames(final_df) <- final_df[1,]
  final_df<-final_df[-1,]
  rownames(final_df)<-NULL
  
  #Return object
  return(final_df)
}
```
TEST
```{r}
request<- get_game_list(start_date="2000-01-01",end_date="2020-12-31",genre="1,2,3",ordering ="-added",n=4)
parse_req <- parse_RAWG(request)
df <- extract_as.df_RAWG(parse_req)

request2 <- get_game_list()
parse_req2 <- parse_RAWG(request2)
df2 <- extract_as.df_RAWG(parse_req2)
```

**Feb 17, 2021**
-Create a similar set of functions for Genres
  1) New get_genre_list function: get_genre_list()
  2) Same parse function: parse_RAWG()
  3) New extract_as.df_genre function: extract_as.df_RAWG_genre()
-Create another set of functions for Games - Achieve
```{r}
library(httr)
library(jsonlite)
library(dplyr)
library(tibble)

get_genre_list<-function(api_key=""){
  #' GET request to RAWG
  #'
  #' Submit RAWG query and receive RAWG response for game genres
  #'
  #' @importFrom httr GET
  #'
  #' @param api_key (str): your api key (recommended - not required, default = none)
  #'
  #' @return Large list containing response from RAWG query
  #'
  #' @examples 
  #' test<-get_genre_list()
  
#Check if API Key is given
  if (api_key == ""){
    cleaned_api_key <- ""
  } else {
    cleaned_api_key <- paste("?key=",api_key,sep="")
  }
  
  link <- paste("https://api.rawg.io/api/genres",api_key,sep="")
  get_link <- GET(link)
  return(get_link)
}

parse_RAWG <- function(get_object){
  #' @title parse the GET request from RAWG 
  #'
  #' @description Convert the GET request from the get_game_list function into a JSON object, making the data available for extraction.
  #'
  #' @importFrom json fromJSON
  #' @import docstring
  #' 
  #' @param get_object (list): Object returned from the GET function
  #'
  #' @return Returns a JSON object containing some general summary data as well as requested data
  #'
  #' @examples raw_data <- parse_RAWG(test)

  raw_content <- fromJSON(content(get_object,"text",encoding="UTF-8"),simplifyVector=FALSE)
  
  #Return object
  return(raw_content)
}

extract_as.df_RAWG_genre <- function(parse_object){
  #' @title extract data from the RAWG JSON object
  #'
  #' @description Extracting the data from 'results' into a dataframe, removing certain fields such as subset of game information, image and following
  #' 
  #' @param parse_object (list): JSON object obtained from the parse_RAWG function
  #' 
  #' @return Returns a dataframe containing the extracted data from the GET function
  #' 
  #' @examples df <- extract_as.df_RAWG_genre(raw_genre)
  
  results <- (raw_genre$results)
  
  #Initial Run
  #Cleanup & Table values for A FIRST GAME
  data_raw <- results[[1]]
  names <- enframe(unlist(data_raw))
  temp_df <- data.frame(names)
  temp_df <- filter(temp_df,!temp_df$name %in% c("games.id","games.slug","games.name","games.added","image_background","following"))
  final_df <- temp_df
  
  for (entries in (2:length(results))){ #Do the same for all other N-1 games 
    #Cleanup & Table values for A SINGLE GENRE 
    data_raw <- results[[entries]]
    names <- enframe(unlist(data_raw))
    temp_df <- data.frame(names)
    temp_df <- filter(temp_df,!temp_df$name %in% c("games.id","games.slug","games.name","games.added","image_background","following"))
      
    #Prepping for merge
    final_df<-full_join(final_df, temp_df, by = "name") #Joining by 'name' column
  }
  
  final_df<-t(final_df)
  colnames(final_df) <- final_df[1,]
  final_df<-final_df[-1,]
  rownames(final_df)<-NULL
  return (final_df)
}
```
TEST
```{r}
library(httr)
library(jsonlite)
library(dplyr)
library(tibble)
request_genre <- get_genre_list()
raw_genre <- parse_RAWG(request_genre)
df <- extract_as.df_RAWG_genre(raw_genre)
```

