---
title: "Introduction"
author: "Aamir M. Khan / Conrad Yeung"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    smart: no
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

RAWG.io.Wrapper is an API wrapper for rawg.io game database website. It allows acquiring detailed information about different games through an easy to use query interface.

## Installation

```{r1 eval=, message=FALSE, warning=FALSE}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("Conrad-Yeung/RAWG.io.Wrapper")
``` 


### Lookup games by genres

Provides a list of all the genres with a count of games available in that category.

```{r, message = FALSE, warning = FALSE}
# library(RAWG.io.Wrapper)
source("../R/game_genre.R")
source("../R/game_list.R")

API_KEY = "95731a37dcf84a638308f6f40fb01801"    # Get you API from RAWG

# Get a list of all genres with some stats
genres <- get_genre_list(API_KEY)

#overview
str(genres)
```

### Lookup a general list of all games

There is another function that returns a list of all the games and allows optional parameters to customize the search.

```{r}

# Get all the games released in the year 2020
query_1 <- get_game_list(api_key=API_KEY,start_date="2020-01-01",end_date="2020-12-31")

str(query_1)
```

```{r}

# Get all the games with ratings between 80 and100
query_2 <- get_game_list(api_key=API_KEY, metacritic="80-100")

str(query_2)
```

