---
title: "Introduction"
author: "Aamir M. Khan / Conrad Yeung"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    smart: no
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

RAWG.io.Wrapper is an API wrapper for rawg.io game database website. It allows acquiring detailed information about different games through an easy to use query interface.

## Installation

```{r}
if (!require("MASS")) install.packages("MASS",repos = "http://cran.us.r-project.org")
if (!require("mgcv")) install.packages("mgcv",repos = "http://cran.us.r-project.org")
if (!require("ggplot2")) install.packages("ggplot2",repos = "http://cran.us.r-project.org")
if (!require("dplyr")) install.packages("dplyr",repos = "http://cran.us.r-project.org")
if (!require("devtools")) install.packages("devtools",repos = "http://cran.us.r-project.org")

library(MASS)
library(mgcv)
library(ggplot2)
library(dplyr)
library(devtools)
install_github("Conrad-Yeung/RAWG.io.Wrapper")
library(RAWG.io.Wrapper)
``` 


### Lookup games by genres

Provides a list of all the genres with a count of games available in that category.

```{r, message = FALSE, warning = FALSE}
API_KEY = "95731a37dcf84a638308f6f40fb01801"    # Get you API from RAWG
# Get a list of all genres with some stats
genres <- get_genre_list(API_KEY)
# Overview
str(genres)
```

We can gain various insights from our query results. So not only the data frames, we can look at graphs for having an idea of trends in data.
```{r}
# Bar chart of the query result
as.data.frame(genres) %>% 
  transform(name=as.factor(name), games_count=as.integer(games_count)) %>%
  ggplot() + aes(x=reorder(name, -games_count), y=games_count) +
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  xlab("Game Genres") +
  ylab("No. of Games") +
  labs(title = "Number of Games Available per Genre")
```


### Lookup a general list of all games

There is another function that returns a list of all the games and allows optional parameters to customize the search.

```{r}
# Get all the games released in the year 2020
query_1 <- get_game_list(api_key=API_KEY,start_date="2020-01-01",end_date="2020-12-31")

str(query_1)
```

```{r}

# Get all the games with ratings between 80 and100
query_2 <- get_game_list(api_key=API_KEY, metacritic="80-100")

str(query_2)
```


We can plot a density graph of the meta-critic ratings to find out what ratings games get on the average from the critics.

```{r}
# Plotting average metacritic ratings
as.data.frame(query_1) %>% 
  ggplot() + aes(x=as.integer(metacritic)) +
  geom_density() +
  xlab("Metacritic Ratings") +
  ylab("Density") +
  labs(title = "Density Plot of Reviewer's Metacritic Ratings")
```































