---
title: "Introduction"
author: "Aamir M. Khan / Conrad Yeung"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    smart: no
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

RAWG.io.Wrapper is an API wrapper for rawg.io game database website. It allows acquiring detailed information about different games through an easy to use query interface.

## Installation

```{r1 eval=, message=FALSE, warning=FALSE}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("Conrad-Yeung/RAWG.io.Wrapper")
``` 


### Lookup games by genres

Provides a list of all the genres with a count of games available in that category.

```{r, message = FALSE, warning = FALSE}
library(ggplot2)
# library(RAWG.io.Wrapper)
source("../R/game_genre.R")
source("../R/game_list.R")

API_KEY = "95731a37dcf84a638308f6f40fb01801"    # Get you API from RAWG

# Get a list of all genres with some stats
genres <- get_genre_list(API_KEY)

# Overview
str(genres)
```

We can various insights from our query results. So not only the data frames, we can look at graphs for having an idea of trends in data.
```{r}
# Bar chart of the query result
as.data.frame(genres) %>% 
  ggplot() + aes(x=as.factor(name), y=as.integer(games_count)) + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  xlab("Game Genres") +
  ylab("Count of Games") +
  labs(title = "Number of Games Available per Genre")
```


### Lookup a general list of all games

There is another function that returns a list of all the games and allows optional parameters to customize the search.

```{r}

# Get all the games released in the year 2020
query_1 <- get_game_list(api_key=API_KEY,start_date="2020-01-01",end_date="2020-12-31")

str(query_1)
```

```{r}

# Get all the games with ratings between 80 and100
query_2 <- get_game_list(api_key=API_KEY, metacritic="80-100")

str(query_2)
```

